Engineering the Servo Web Browser Engine using Rust

### 2015-10-24 icse16-servo/open.tex
Add conclusion. Fix typos.

\subsection{Incremental computation} As mentioned in \secref{sec:browsers},
all modern browsers use some combination of dirty bit marking and incremental
recomputation heuristics to avoid reprocessing the full page when
a mutatation is performed.
Unfortunately, these heuristics are not only frequently the source of
performance differences between browsers, but they are also a source of
correctness bugs.
A library that provided a form of self adjusting computation suited to
incremental recomputation of only the visible part of the page, perhaps
based on the Adapton~\cite{adapton} approach, seems promising.

>>>>

\subsection{Incremental computation} As mentioned in \secref{sec:browsers},
all modern browsers use some combination of dirty bit marking and incremental
recomputation heuristics to avoid reprocessing the full page when
a mutation is performed.
Unfortunately, these heuristics are not only frequently the source of
performance differences between browsers, but they are also a source of
correctness bugs.
A library that provided a form of self adjusting computation suited to
incremental recomputation of only the visible part of the page, perhaps
based on the Adapton~\cite{adapton} approach, seems promising.
